---
title: "p8105_hw1_nl2655"
author: "Nankun"
output: github_document
---


# Problem 1



```{r}
library(tidyverse)
set.seed(1551)

p1_df = tibble(
  norm_samp = rnorm(8),
  vec_logical = norm_samp>0,
  vec_char = c("LENGTH_1","LENGTH_2","LENGTH_3","LENGTH_4","LENGTH_5","LENGTH_6","LENGTH_7","LENGTH_8"),
  vec_factor = factor(c("l","m","s","s","m","l","m","s"))
)

mean(pull(p1_df, norm_samp))
mean(pull(p1_df, vec_logical))
mean(pull(p1_df, vec_char))
mean(pull(p1_df, vec_factor))
```

From the result of Knit, the mean of sample is -0.76, the mean of logical vector is 0.375.
The character vector and the factor vector cannot working on mean.




```{r,results='hide'}
as.numeric(pull(p1_df, vec_logical))
as.numeric(pull(p1_df, vec_char))
as.numeric(pull(p1_df, vec_factor))
```

The logical vector are successfully convert to numeric vector, because it is binary variable that can be converted to the number "1" and "0". 
factor vector are successfully convert to numeric vector, because the factor vector is categorical variable that can be converted to the orderal numbers.
But character vertor failed, because the names cannot be seen as any kind of numbers.

This partly explain the situation happen when take the mean. The character vector cannot be converted 
to numeric, thus it cannot be taken mean.





